### 2019-12-11 introduction.tex
Final draft

\chapter{Introduction} \label{chap:introduction}
\section{Overview} \label{sec:introduction_overview}
The \textit{standard model} (SM; sec.~\ref{sec:introduction_standard_model}) of particle physics is our current best mathematical framework for describing the behavior
of elementary particles. The domain of applicability of the SM is quite substantial, encompassing
every well-measured fundamental interaction of every verified fundamental particle. All SM particles have been conclusively observed,
and no fundamental particles outside the SM have ever been conclusively observed. After decades of effort by thousands of researchers,
no significant deviation from SM predictions has ever been confirmed in high-energy scattering experiments~\cite{ref:CahnGoldhaber, ref:PDG}.
These efforts are extended here with a study of the relationship between two particles, \PZ\ and \Pgamma, at state-of-the-art precision
(sec.~\ref{sec:introduction_znng}).

@@

Specifically, this thesis presents several analyses of event yields in \textit{monophoton} final states, characterized by a single \Pgamma\ with
high transverse momentum, along with an overall transverse momentum imbalance typically of equal magnitude and opposite direction to
that of the \Pgamma.

@@

These interactions lead to the relationships illustrated in Fig.~\ref{fig:sm_interactions}, in which every linkage represents
a direct \textit{coupling}, which allows a particle at one end of the link to evolve directly into a particle at the other end.
Particles with a nonzero electric charge are all coupled directly to the photon. The photon is coupled to the weak bosons
(\PZ\ and $W^\pm$), which in turn couple to all of the fundamental fermions. The gluons couple directly with each other and with the quarks.
Particles that couple directly to the \PH\ have an intrinsic mass (specified by the top number in each square of Fig.~\ref{fig:sm_particles}\footnote{The
proper units of mass are $\mathrm{GeV}\,c^{2}$, but the factor of $c^{2}$ is often omitted for brevity. This is done even when units of distance and
time (such as cm and ns) are used in which $c$ does not equal 1. Similarly, the factor of $1/c$ is often omitted from the proper units of momentum,
$\mathrm{GeV}/c$. This is the convention followed in this thesis.}) tied to the strength of their coupling.
In the SM, any particle that does not couple directly to the \PH\ is massless.

@@

However, the mass of the proton is much greater than the sum of the masses of these three components, and this additional mass is associated with an effervescent
``sea'' of \textit{partons}, transient particles swarming the proton that can only be distinguished at high energies.
Known partons include gluons (carrying about 50\% of the total momentum of a high-energy proton),
all types of quark and antiquark, and photons. As a consequence, a high-energy collision between two protons can give rise to a $q\bar{q}$ interaction,
which is the primary catalyst for all the processes studied below. A single parton carries some fraction of the total energy carried by the whole proton,
so in general, partons collide with a lower interaction energy than that of the protons that carry them.
The square of the center-of-mass energy of colliding protons is denoted by $s$, while that of a specific
parton-parton interaction is denoted by $\hat{s}$.

@@

\subsection{Previous measurements} \label{sec:introduction_znng_previous_measurements}
Experiments at the LEP detector measured the cross section of \zinvg\ arising from $e^{\mathrm{+}}e^{\mathrm{-}}$ collisions for $\sqrt{s}$ up to \textasciitilde200 GeV.
The L3 experiment measured the cross section to be $5.1 \pm 0.3\mathrm{(stat)} \pm 0.1\mathrm{(syst)}$ $pb$ based on 175.6 $pb^{-1}$ of collision data with an average $\sqrt{s} = 188.6$ GeV, compared to an SM
prediction of $4.99 \pm 0.05\mathrm{(stat)}$~\cite{ref:j.physletb.2004.07.002}. Looking at collision data at the same $\sqrt{s}$, but with different cuts,
the OPAL experiment measured the cross section to be $2.52 \pm 0.13\mathrm{(stat)} \pm 0.05\mathrm{(syst)}$ $pb$ based on 177.3 $pb^{-1}$ of data, compared to an SM
prediction of $2.81 \pm 0.02\mathrm{(stat)}$ $pb$~\cite{ref:s100520000490}. This set of SM predictions were made up to $O(\alpha^2)$, but LO in $\alpha_\mathrm{S}$.

The D0 experiment at the Tevatron made the first observation of \zinvg\ arising from $p\bar{p}$ collisions in 2009. This yielded a cross section measurement of
$32 \pm 9\mathrm{(stat+syst)} \pm 2\mathrm{(lumi)}$ $fb$ for a leading photon \pT\ above 90\unit{GeV}\footnote{The proper units for momentum are $\mathrm{GeV}/c$, but the
factor of $c$ is often omitted for brevity, and this is the convention followed in this thesis. Similarly, the proper units for mass are $\mathrm{GeV}\,c^{2}$, but the factor
of $c^{2}$ is usually omitted.},
compared to an SM prediction of $39 \pm 4\mathrm{(theory)}$ $fb$ computed to NLO in $\alpha_\mathrm{S}$~\cite{ref:PhysRevLett.102.201802}.

Measurements of the cross section at higher values of \pTgamma\ have been performed by experiments examining \Pp\Pp\ collision data at the LHC.
An analysis by the CMS experiment examining 19.6\fbinv\ of data collected at $\sqrt{s} = 8\unit{TeV}$ found the observed \zinvg\ cross section for $\pTgamma > 145\unit{GeV}$ to be
$52.7 \pm 2.1\mathrm{(stat)} \pm 6.4\mathrm{(syst)} \pm 1.4\mathrm{(lumi)}$ $fb$, compared to an SM prediction of $40.7 \pm 4.9\mathrm{(theory)}$ $fb$ calculated to NLO in $\alpha_\mathrm{S}$, and
a prediction of $50.0^{+2.4}_{-2.2}\mathrm{(theory)}$ calculated to NNLO in $\alpha_\mathrm{S}$~\cite{ref:j.physletb.2016.06.080}. This comparison illustrates the need for NNLO precision at high \pTgamma.

The most precise measurement of the \zinvg\ cross section for \pTgamma\ and \MET\ above 150\unit{GeV} currently comes from an analysis of 36.1\fbinv\ of \Pp\Pp\ collision data
collected by the ATLAS experiment at $\sqrt{s} = 13\unit{TeV}$, with an observed cross section of $83.7^{+3.6}_{-3.5}\mathrm{(stat)}^{+6.9}_{-6.2}\mathrm{(syst)}^{+1.7}_{-2.0}\mathrm{(lumi)}$ $fb$.
The corresponding SM prediction, computed to NNLO in $\alpha_\mathrm{S}$ using the MATRIX generator~\cite{ref:epjc/s10052-018-5771-7}, is $78.6 \pm 0.4\mathrm{(stat)} \pm 4.1\mathrm{(syst)}$ $fb$~\cite{ref:CERN-EP-2018-220}.
The cross section is shown in discrete ranges (bins) of leading photon \pT\ in Fig.~\ref{fig:znng_xsec_phoET_ATLAS}.

@@

\begin{figure}[hbtb]
  \begin{center}
    \includegraphics[width=0.49\textwidth]{Figures/dmsimp_ichep2018_av.png}
    \includegraphics[width=0.49\textwidth]{Figures/dmsimp_ichep2018_v.png}
    \caption{Summary plots of limits on DM simplified model parameters, shown in~\cite{ref:dmsummaryplots_ichep2018}. Simplified models are excluded at 95\% CL or above
    for parameter values under the contours.
    Results based on three different final states are shown: mono-$Z(ll)$~\cite{ref:epjc/s10052-018-5740-1} in yellow, mono-$j/V(qq)$~\cite{ref:PhysRevD.97.092005} in red, and monophoton~\cite{ref:1810.00196} in blue,
    the latter corresponding to the new results presented in this thesis. The $\Omega_\mathrm{c}^{2}$ curves correspond to constraints on the cosmological DM abundance set by Planck satellite measurements~\cite{ref:planck2018_cosparams}.}
    \label{fig:dmsimp_ichep2018}
  \end{center}
\end{figure}

Prior to the analysis presented in this thesis, the last published results from CMS in the monophoton final state examined 12.9\fbinv\ of data collected in the first half
of 2016~\cite{ref:JHEP10(2017)073}. Simplified models were excluded at 95\% CL for \mmed\ up to 700 GeV at small values of \mdm, in both the vector
and axial-vector cases. Values of $\Lambda$ for the DM-EWK EFT up to 600 GeV were also excluded at 95\% CL, assuming $k_{1} = k_{2} = 1$\footnote{Defining $k = \sqrt{k_{1}^{2} + k_{2}^{2}}$
and $\theta_{k} = \arctan{\frac{k_{2}}{k_{1}}}$, the choice $k_{1} = k_{2} = 1$ corresponds to the choice $k = \sqrt{2}$ and $\theta_{k} = \pi/4$. Fixing $\theta_{k} = \pi/4$,
the limits on $\Lambda / k^{1/3}$ for arbitrary $k$ are equal to the $k = \sqrt{2}$ limits on $\Lambda$ multiplied by $2^{-1/6}$.}.

The most stringent monophoton results to date are set by an analysis of 36.1\fbinv\ of data collected by the ATLAS detector~\cite{ref:epjc/s10052-017-4965-8}.
Simplified models were excluded at 95\% CL for \mmed\ up to 1200 GeV at small values of \mdm, in both the vector and axial-vector cases, as shown in Fig.~\ref{fig:dmsimp_atlas}.
Values of $\Lambda$ for the DM-EWK EFT up to 790 GeV, assuming $k_{1} = k_{2} = 1$, were also excluded at 95\% CL, as shown in Fig.~\ref{fig:dmeft_atlas}.

@@

\begin{figure}[hbtb]
  \begin{center}
    \includegraphics[width=0.49\textwidth]{Figures/dmeft_atlas.png}
    \caption{Limits on the DM-EWK EFT set by the ATLAS experiment, as shown in~\cite{ref:epjc/s10052-017-4965-8}. The DM-EWK EFT is excluded at 95\% CL or above for
    values of $\Lambda$ under the contour.
    }
    \label{fig:dmeft_atlas}
  \end{center}
\end{figure}

\begin{figure}[hbtb]
  \begin{center}
    \includegraphics[width=0.98\textwidth]{Figures/dmsimp_dd_atlas.png}
    \caption{Limits on low-energy DM-nucleon scattering cross sections set by the ATLAS experiment, as shown in~\cite{ref:epjc/s10052-017-4965-8}. The ATLAS
    limits are compared against limits on the SD cross section from PICO-60~\cite{ref:PICO60-ATLAS} and LUX~\cite{ref:LUX-SD-ATLAS} (left)
    and limits on the SI cross section from PandaX-II~\cite{ref:PANDAX-II-ATLAS}, LUX~\cite{ref:LUX-SI-ATLAS}, CRESST-II~\cite{ref:CRESST-II-ATLAS}, and CDMSlite~\cite{ref:SuperCDMS-ATLAS} (right).
    Scattering cross sections are excluded at 90\% CL or more above the contours.
    }
    \label{fig:dmsimp_dd_atlas}
  \end{center}
\end{figure}

@@

\section{ADD gravitons} \label{sec:introduction_ADD}
We finally examine a model of gravitation in extra dimensions originally proposed by Arkani-Hamed, Dimoupolos, and Dvali (ADD)~\cite{ref:S0370-2693(98)00466-3}.
Gravity typically affects SM particles much, much less than the other fundamental interactions. The weakness of gravity
is often expressed in terms of a fundmental mass scale \mPl\ (\textasciitilde$10^{19}$ GeV), which is
many orders of magnitude larger than the masses of the EWK bosons (\textasciitilde$10^{2}$ GeV). Particle-level gravitational interactions
are correspondingly sharply suppressed. The proposed boson of gravitation, the graviton, has yet to be detected and is not part of the SM.
The mystery of why \mPl\ is so much larger than the EWK mass scale has been called the ``Hierarchy problem,'' and the desire for a
more elegant formulation has been a productive stimulus for BSM theories~\cite{ref:S0370-2693(98)00466-3, ref:0264-9381/32/3/033001}.

@@

>>>>

\chapter{Introduction} \label{chap:introduction}
\section{Overview} \label{sec:introduction_overview}
The \textit{standard model} (SM; sec.~\ref{sec:introduction_standard_model}) of particle physics is our current best mathematical framework for describing the behavior
of elementary particles. The domain of applicability of the SM is quite substantial, encompassing
every well-measured fundamental interaction of every verified fundamental particle. All SM particles have been conclusively observed,
and no fundamental particles outside the SM have ever been conclusively observed. The rigorous theoretical development and experimental confirmation of the SM
has spanned decades of effort by thousands of researchers~\cite{ref:CahnGoldhaber, ref:PDG}.
These efforts are extended here with a study of the relationship between two particles, \PZ\ and \Pgamma, at state-of-the-art precision
(sec.~\ref{sec:introduction_znng}).

@@

Specifically, this thesis presents several analyses of event yields in \textit{monophoton} final states, characterized by a single \Pgamma\ with
high transverse momentum, along with an overall transverse momentum imbalance typically of equal magnitude and opposite direction to
that of the \Pgamma. The photon in these events gives a visible indicator of the production of difficult-to-detect particles emerging in the opposite direction,
such as neutrinos, in the case of SM \zinvg\ events, or potentially BSM particles such as DM or gravitons.

@@

These interactions lead to the relationships illustrated in Fig.~\ref{fig:sm_interactions}, in which every linkage represents
a direct \textit{coupling}, which allows a particle at one end of the link to evolve directly into a particle at the other end.
Particles with a nonzero electric charge are all coupled directly to the photon. The photon is coupled to the weak bosons
(\PZ\ and $W^\pm$), which in turn couple to all of the fundamental fermions. The gluons couple directly with each other and with the quarks.
Particles that couple directly to the \PH\ have an intrinsic mass (specified by the top number in each square of Fig.~\ref{fig:sm_particles}\footnote{The
proper units of mass are $\mathrm{GeV}\,c^{2}$, but the factor of $c^{2}$ is often omitted. This is done even when, elsewhere, units of distance and
time (such as cm and ns) are quoted in which $c$ does not equal 1. Similarly, the factor of $1/c$ is often omitted from the proper units of momentum,
$\mathrm{GeV}/c$. Units are chosen based on their elegance and convenience relating to the quantity being reported; expressions without $c$ factors
may be more concisely expressed, and they render more transparently the close connection between energy, momentum, and mass.
In cases where an explicit $c$ factor is omitted, it may be assumed that units are implicitly being chosen in which $c$ is exactly 1.
This is the convention followed in this thesis.}) tied to the strength of their coupling.
In the SM, any particle that does not couple directly to the \PH\ is massless.

@@

However, the mass of the proton is much greater than the sum of the masses of these three components, and this additional mass is associated with an effervescent
``sea'' of \textit{partons}, transient particles swarming the proton that can only be distinguished at high energies.
Known partons include gluons (carrying about 50\% of the total momentum of a high-energy proton),
all types of quark and antiquark, and photons. As a consequence, a high-energy collision between two protons can give rise to a $q\bar{q}$ interaction,
which is the primary catalyst for all the processes studied below. A single parton carries some fraction of the total energy carried by the whole proton,
so in general, partons collide with a lower interaction energy than that of the protons that carry them.
The square of the center-of-mass energy of colliding protons is denoted by $s$, while that of a specific
parton--parton interaction is denoted by $\hat{s}$.

@@

\subsection{Previous measurements} \label{sec:introduction_znng_previous_measurements}
Experiments at the LEP detector measured the cross section of \zinvg\ arising from $e^{\mathrm{+}}e^{\mathrm{-}}$ collisions for $\sqrt{s}$ up to \textasciitilde200 GeV.
The L3 experiment measured the cross section to be $5.1 \pm 0.3\mathrm{(stat)} \pm 0.1\mathrm{(syst)}\unit{pb}$ based on $175.6\unit{pb}^{-1}$ of collision data with an average $\sqrt{s} = 188.6\unit{GeV}$, compared to an SM
prediction of $4.99 \pm 0.05\mathrm{(stat)}\unit{pb}$~\cite{ref:j.physletb.2004.07.002}. Looking at collision data at the same $\sqrt{s}$, but with different cuts,
the OPAL experiment measured the cross section to be $2.52 \pm 0.13\mathrm{(stat)} \pm 0.05\mathrm{(syst)}\unit{pb}$ based on $177.3\unit{pb}^{-1}$ of data, compared to an SM
prediction of $2.81 \pm 0.02\mathrm{(stat)}\unit{pb}$~\cite{ref:s100520000490}. This set of SM predictions were made up to $O(\alpha^2)$, but LO in $\alpha_\mathrm{S}$.

The D0 experiment at the Tevatron made the first observation of \zinvg\ arising from $p\bar{p}$ collisions in 2009. This yielded a cross section measurement of
$32 \pm 9\mathrm{(stat+syst)} \pm 2\mathrm{(lumi)}\unit{fb}$ for a leading photon \pT\ above 90\unit{GeV},
compared to an SM prediction of $39 \pm 4\mathrm{(theory)}\unit{fb}$ computed to NLO in $\alpha_\mathrm{S}$~\cite{ref:PhysRevLett.102.201802}.

Measurements of the cross section at higher values of \pTgamma\ have been performed by experiments examining \Pp\Pp\ collision data at the LHC.
An analysis by the CMS experiment examining 19.6\fbinv\ of data collected at $\sqrt{s} = 8\unit{TeV}$ found the observed \zinvg\ cross section for $\pTgamma > 145\unit{GeV}$ to be
$52.7 \pm 2.1\mathrm{(stat)} \pm 6.4\mathrm{(syst)} \pm 1.4\mathrm{(lumi)}\unit{fb}$, compared to an SM prediction of $40.7 \pm 4.9\mathrm{(theory)}\unit{fb}$ calculated to NLO in $\alpha_\mathrm{S}$, and
a prediction of $50.0^{+2.4}_{-2.2}\mathrm{(theory)}\unit{fb}$ calculated to NNLO in $\alpha_\mathrm{S}$~\cite{ref:j.physletb.2016.06.080}. This comparison illustrates the need for NNLO precision at high \pTgamma.

The most precise measurement of the \zinvg\ cross section for \pTgamma\ and \MET\ above 150\unit{GeV} currently comes from an analysis of 36.1\fbinv\ of \Pp\Pp\ collision data
collected by the ATLAS experiment at $\sqrt{s} = 13\unit{TeV}$, with an observed cross section of $83.7^{+3.6}_{-3.5}\mathrm{(stat)}^{+6.9}_{-6.2}\mathrm{(syst)}^{+1.7}_{-2.0}\mathrm{(lumi)}\unit{fb}$.
The corresponding SM prediction, computed to NNLO in $\alpha_\mathrm{S}$ using the MATRIX generator~\cite{ref:epjc/s10052-018-5771-7}, is $78.6 \pm 0.4\mathrm{(stat)} \pm 4.1\mathrm{(syst)}\unit{fb}$~\cite{ref:CERN-EP-2018-220}.
The cross section is shown in discrete ranges (bins) of leading photon \pT\ in Fig.~\ref{fig:znng_xsec_phoET_ATLAS}.

@@

\begin{figure}[hbtb]
  \begin{center}
    \includegraphics[width=0.49\textwidth]{Figures/dmsimp_ichep2018_av.png}
    \includegraphics[width=0.49\textwidth]{Figures/dmsimp_ichep2018_v.png}
    \caption{Summary plots of limits on DM simplified model parameters, shown in~\cite{ref:dmsummaryplots_ichep2018}. Simplified models are excluded at 95\% CL or above
    for parameter values under the contours.
    Results based on three different final states are shown: mono-$Z(ll)$~\cite{ref:epjc/s10052-018-5740-1} in yellow, mono-$j/V(qq)$~\cite{ref:PhysRevD.97.092005} in red, and monophoton~\cite{ref:JHEP02(2019)074} in blue,
    the latter corresponding to the new results presented in this thesis. The $\Omega_\mathrm{c}^{2}$ curves correspond to constraints on the cosmological DM abundance set by Planck satellite measurements~\cite{ref:planck2018_cosparams}.}
    \label{fig:dmsimp_ichep2018}
  \end{center}
\end{figure}

Prior to the analysis presented in this thesis, the last published results from CMS in the monophoton final state examined 12.9\fbinv\ of data collected in the first half
of 2016~\cite{ref:JHEP10(2017)073}. Simplified models were excluded at 95\% CL for \mmed\ up to 700\unit{GeV} at small values of \mdm, in both the vector
and axial-vector cases. Values of $\Lambda$ for the DM-EWK EFT up to 600\unit{GeV} were also excluded at 95\% CL, assuming $k_{1} = k_{2} = 1$\footnote{Defining $k = \sqrt{k_{1}^{2} + k_{2}^{2}}$
and $\theta_{k} = \arctan{\frac{k_{2}}{k_{1}}}$, the choice $k_{1} = k_{2} = 1$ corresponds to the choice $k = \sqrt{2}$ and $\theta_{k} = \pi/4$. Fixing $\theta_{k} = \pi/4$,
the limits on $\Lambda / k^{1/3}$ for arbitrary $k$ are equal to the $k = \sqrt{2}$ limits on $\Lambda$ multiplied by $2^{-1/6}$.}.

The most stringent monophoton results to date are set by an analysis of 36.1\fbinv\ of data collected by the ATLAS detector~\cite{ref:epjc/s10052-017-4965-8}.
Simplified models were excluded at 95\% CL for \mmed\ up to 1200\unit{GeV} at small values of \mdm, in both the vector and axial-vector cases, as shown in Fig.~\ref{fig:dmsimp_atlas}.
Values of $\Lambda$ for the DM--EWK EFT up to 790\unit{GeV}, assuming $k_{1} = k_{2} = 1$, were also excluded at 95\% CL, as shown in Fig.~\ref{fig:dmeft_atlas}.

@@

\begin{figure}[hbtb]
  \begin{center}
    \includegraphics[width=0.49\textwidth]{Figures/dmeft_atlas.png}
    \caption{Limits on the DM--EWK EFT set by the ATLAS experiment, as shown in~\cite{ref:epjc/s10052-017-4965-8}. The DM--EWK EFT is excluded at 95\% CL or above for
    values of $\Lambda$ under the contour.
    }
    \label{fig:dmeft_atlas}
  \end{center}
\end{figure}

\begin{figure}[hbtb]
  \begin{center}
    \includegraphics[width=0.98\textwidth]{Figures/dmsimp_dd_atlas.png}
    \caption{Limits on low-energy DM--nucleon scattering cross sections set by the ATLAS experiment, as shown in~\cite{ref:epjc/s10052-017-4965-8}. The ATLAS
    limits are compared against limits on the SD cross section from PICO-60~\cite{ref:PICO60-ATLAS} and LUX~\cite{ref:LUX-SD-ATLAS} (left)
    and limits on the SI cross section from PandaX-II~\cite{ref:PANDAX-II-ATLAS}, LUX~\cite{ref:LUX-SI-ATLAS}, CRESST-II~\cite{ref:CRESST-II-ATLAS}, and CDMSlite~\cite{ref:SuperCDMS-ATLAS} (right).
    Scattering cross sections are excluded at 90\% CL or more above the contours.
    }
    \label{fig:dmsimp_dd_atlas}
  \end{center}
\end{figure}

@@

\section{ADD gravitons} \label{sec:introduction_ADD}
We finally examine a model of gravitation in extra dimensions originally proposed by Arkani-Hamed, Dimoupolos, and Dvali (ADD)~\cite{ref:S0370-2693(98)00466-3}.
Gravity typically affects SM particles much, much less than the other fundamental interactions. The weakness of gravity
is often expressed in terms of a fundmental mass scale \mPl\ (\textasciitilde$10^{19}\unit{GeV}$), which is
many orders of magnitude larger than the masses of the EWK bosons (\textasciitilde$10^{2}\unit{GeV}$). Particle-level gravitational interactions
are correspondingly sharply suppressed. The proposed boson of gravitation, the graviton, has yet to be detected and is not part of the SM.
The mystery of why \mPl\ is so much larger than the EWK mass scale has been called the ``Hierarchy problem,'' and the desire for a
more elegant formulation has been a productive stimulus for BSM theories~\cite{ref:S0370-2693(98)00466-3, ref:0264-9381/32/3/033001}.

@@

In this thesis, monophoton events are examined in 35.9\fbinv\ of 13\unit{TeV} \Pp\Pp\ collision data collected by the CMS experiment in 2016.
From these, the differential \zinvg\ cross section at 13\unit{TeV} is measured as a function of \pTgamma. Limits are set on model
parameters of the DM--EWK EFT, DM simplified models, and the ADD model.

### 2019-12-11 results.tex
Final draft

\begin{table}
\centering
\begin{tabular}{ cccc }
\hline
\pTgamma\ range [GeV] & Cross section [fb] & Syst Unc. [fb] & Stat Unc. [fb] \\
\hline
175-200 & 13.8 & 1.4 (9.9\%) & 2.2 (16\%) \\
200-250 & 14.4 & 1.0 (7.2\%) & 1.8 (12\%) \\
250-300 & 7.4 & 1.2 (16\%) & 1.2 (17\%) \\
300-400 & 5.52 & 0.47 (8.6\%) & 0.98 (18\%) \\
400-600 & 3.31 & 0.15 (4.6\%) & 0.65 (20\%) \\
600-Inf & 1.18 & 0.04 (3.4\%) & 0.36 (31\%) \\
\hline
\end{tabular}
\caption{Measured \zinvg\ cross section in bins of \pTgamma.
The combined uncertainty arising from all constrained nuisance parameters in the likelihood fit is denoted by ``Syst Unc.'', while
uncertainty corresponding to the limited size of the observed data set is denoted by ``Stat Unc.''}
\label{tab:measured_xsec}
\end{table}

@@

The theoretical SM prediction, as computed in MATRIX to NNLO in $\alpha_\mathrm{S}$, is listed for each true \pTgamma\ bin in Table~\ref{tab:matrix_xsec}, which
also lists the uncertainties on the prediction due to the choice of renormalization and factorization scales (scale uncertainty). Figure~\ref{fig:measvsmat}
compares the measured cross section to the MATRIX predictions.
The two generally agree to within the statistical errors of the measurement, except in the highest \pTgamma\ bins: the difference
between the measured and predicted cross section in the 400-600\unit{GeV} bin is 1.6 times the statistical error on the measurement, and the difference
for the 600-Inf bin is 1.8 times the statistical error. The \zinvg\ process contributes an estimated 14.12 events to the observed 16 events in the 600-Inf bin.
Under the hypothesis that the MATRIX prediction is true, the probability of observing at least 14 \zinvg\ events
from the 600-Inf bin is about 1\%\footnote{Assuming that these events are produced via a Poisson process with mean
$\sigma_\mathrm{MATRIX}*L = 19.71$ and that each produced event is observed with probability 0.3508 (estimated in MC).}.
This falls far short of the standard ``$5\sigma$'' (about 0.00003\%) criterion for rejecting the SM and claiming discovery of new physics, in particular
since the look-elsewhere effect~\cite{ref:08-AOAS163} is not being accounted for and also since no specific BSM model is being compared here.
However, it does indicate a notable tension with the MATRIX NNLO predictions that should be kept in mind in future studies.

@@

Upper limits on the cross section for the DM-EWK EFT model are translated into the lower limits on the suppression scale $\Lambda$, shown in
Fig.~\ref{fig:DMEWKlimits}. The EFT hypothesis is excluded at $95\%$ CL or above for values of $\Lambda$ up to 850\unit{GeV} (observed), 950\unit{GeV}
(expected), at small \mdm\ values.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=7.5cm,height=7.0cm]{figures/exo16053/Figure_009.pdf}
\caption{The 95\% CL observed and expected lower limits on $\Lambda$ for the DM-EWK EFT model, shown as a function of \mdm.
Published in~\cite{ref:JHEP02(2019)074}.}
\label{fig:DMEWKlimits}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.5\textwidth]{figures/exo16053/Figure_010.pdf}
    \caption{The 95\% CL upper limits on the ADD graviton production cross section, as a function of \mD\, for $n=3$ extra dimensions.
    Published in~\cite{ref:JHEP02(2019)074}.}
    \label{fig:ADDLimits}
  \end{center}
\end{figure}

>>>>

\begin{table}
\centering
\begin{tabular}{ cccc }
\hline
\pTgamma\ range [GeV] & Cross section [fb] & Syst Unc. [fb] & Stat Unc. [fb] \\
\hline
175-200 & 13.0 & 1.1 (8.7\%) & 1.8 (14\%) \\
200-250 & 14.2 & 0.9 (6.6\%) & 1.6 (11\%) \\
250-300 & 7.3 & 1.1 (15\%) & 1.1 (15\%) \\
300-400 & 5.50 & 0.44 (8.0\%) & 0.92 (17\%) \\
400-600 & 3.31 & 0.15 (4.4\%) & 0.63 (19\%) \\
600-Inf & 1.18 & 0.03 (2.8\%) & 0.36 (30\%) \\
\hline
\end{tabular}
\caption{Measured \zinvg\ cross section in bins of \pTgamma.
The combined uncertainty arising from all constrained nuisance parameters in the likelihood fit is denoted by ``Syst Unc.'', while
uncertainty corresponding to the limited size of the observed data set is denoted by ``Stat Unc.''}
\label{tab:measured_xsec}
\end{table}

@@

The theoretical SM prediction, as computed in MATRIX to NNLO in $\alpha_\mathrm{S}$, is listed for each true \pTgamma\ bin in Table~\ref{tab:matrix_xsec}, which
also lists the uncertainties on the prediction due to the choice of renormalization and factorization scales (scale uncertainty). Figure~\ref{fig:measvsmat}
compares the measured cross section to the MATRIX predictions.
The two generally agree to within the statistical errors of the measurement, except in the highest \pTgamma\ bins: the difference
between the measured and predicted cross section in the 400-600\unit{GeV} bin is 1.6 times the statistical error on the measurement, and the difference
for the 600-Inf bin is 1.8 times the statistical error. The \zinvg\ process contributes an estimated 13.6 events to the observed 16 events in the 600-Inf bin.
Under the hypothesis that the MATRIX prediction is true, the probability of detecting at least 14 \zinvg\ events
in the 600-Inf bin is about 1\%\footnote{Assuming that \zinvg\ events with true $\pTgamma < 600\unit{GeV}$ contribute negligibly many observed events to this bin
on average (as indicated by the response matrix, Tab.~\ref{tab:response_matrix_values}), and that \zinvg\ events with true $\pTgamma > 600\unit{GeV}$ are produced via a
Poisson process with mean $\sigma_\mathrm{MATRIX}*L = 19.7$ and each such event is detected with probability 0.35 (estimated in MC).}.
This falls far short of the standard ``$5\sigma$'' (about 0.00003\%) criterion for rejecting the SM and claiming discovery of new physics, in particular
since the look-elsewhere effect~\cite{ref:08-AOAS163} is not being accounted for and also since no specific BSM model is being compared here.
However, it does indicate a notable tension with the MATRIX NNLO predictions that should be kept in mind in future studies.

@@

Upper limits on the cross section for the DM--EWK EFT model are translated into the lower limits on the suppression scale $\Lambda$, shown in
Fig.~\ref{fig:DMEWKlimits}. The EFT hypothesis is excluded at $95\%$ CL or above for values of $\Lambda$ up to 850\unit{GeV} (observed), 950\unit{GeV}
(expected), at small \mdm\ values.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=7.5cm,height=7.0cm]{figures/exo16053/Figure_009.pdf}
\caption{The 95\% CL observed and expected lower limits on $\Lambda$ for the DM--EWK EFT model, shown as a function of \mdm.
Published in~\cite{ref:JHEP02(2019)074}.}
\label{fig:DMEWKlimits}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.5\textwidth]{figures/exo16053/add.png}
    \caption{The 95\% CL upper limits on the ADD graviton production cross section, as a function of \mD\, for $n=3$ extra dimensions.
    Published in~\cite{ref:JHEP02(2019)074}.}
    \label{fig:ADDLimits}
  \end{center}
\end{figure}
